Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-09 tex/body.tex
simpler

\newcommand\badassex{%
 \{\forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ),\;\,
 \forallf{\con{g}} x.\;\, \lite( \con{f}( x ) \teq 5,\allowbreak\;
   \con{g}( x ) \teq \con{f}( x ),\allowbreak\;
   \con{g}( x ) \teq \con{g}( x ) + 1)\}}

An example of an inadmissible function set is
$\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) + 1 \}$,
since the formula $\ltrue$ is (trivially) closed under function expansion with respect to this set,
and there is no model of $T$
satisfying $\con{f}$'s definition. A more subtle specimen is
\begin{shortv}$\badassex$. \end{shortv}%
\begin{longv}\[\badassex\]\end{longv}%
While this set has a model where $\con f$ and $\con g$ are interpreted as the
constant function $5$, it is not admissible since %the formula
$\con{f}( 0 ) \teq 4$ is
closed under function expansion \begin{longv}with respect to this set\end{longv}
and yet there exists
no interpretation satisfying both $\con{f}( 0 ) \teq 4$ and $\con{g}$'s
definition.

>>>>

%\newcommand\badassex{
% \{\forallf{\con{f}} x : \typeint.\;\, \con{f}( x ) \teq \con{f}( x ),\;\,
% \forallf{\con{g}} x : \typeint.\;\, \lite( \con{f}( x ) \teq 5,\allowbreak\;
%   \con{g}( x ) \teq \con{f}( x ),\allowbreak\;
%   \con{g}( x ) \teq \con{g}( x ) + 1)\}}
\newcommand\badassex{
 \{\forallf{\con{f}} x : \typeint.\;\, \con{f}( x ) \teq \con{f}( x ),\;\,
 \forallf{\con{g}} x : \typeint.\;\, \con{g}( x ) \teq \con{g}( x ) + \nobreak\con{f}( x )\}}

An example of an inadmissible set is
$\{ \forallf{\con{f}} x : \typeint.\;\, \con{f}( x ) \teq \con{f}( x ) + 1 \}$,
since the formula $\ltrue$ is (trivially) closed under function expansion with respect to this set,
and there is no model of $T$
satisfying $\con{f}$'s definition. A more subtle specimen is
\begin{shortv}$\badassex$. \end{shortv}%
\begin{longv}\[\badassex\]\end{longv}%
While this set has a model where $\con f$ and $\con g$ are interpreted as the
constant function $0$, it is not admissible since %the formula
$\con{f}( 0 ) \teq 1$ is
closed under function expansion \begin{longv}with respect to this set\end{longv}
and yet there exists
no interpretation satisfying both $\con{f}( 0 ) \teq 1$ and $\con{g}$'s
definition.
